---
title: "Examining Racial Disparities in U.S. Incarceration and Capital Punishment"
author: 
  - name: Zoe Williams
    affil: 1
  - name:  Nathan Alexander, PhD
    affil: 2, 3
affiliation:
  - num: 1
    address: Department of Political Science, College of Arts and Sciences
  - num: 2
    address: Department of Curriculum and Instruction, School of Education
  - num: 3
    address: Program in Applied Data Science and Analytics, The Graduate School
column_numbers: 3
logoright_name: img/qs-logo.png
logoleft_name: img/hu-logo.jpg
titlebox_borderwidth: "0.25cm"
primary_colour: "#ffffff"
secondary_colour: "#5F6062"
accent_colour: "#E51937"
titlebox_bordercol: "#003A63"
title_textcol: "#003A63"
author_textcol: "#003A63"
affiliation_textcol: "#003A63"
columnline_col: "#E51937"
columnline_style: solid
sectitle_textcol: "#ffffff"
sectitle_bgcol: "#003A63"
sectitle_bordercol: "#003A63"
sectitle2_textcol: "#003A63"
output: 
  - posterdown::posterdown_html
bibliography: references.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#install.packages("pak")
#install.packages("posterdown")
pak::pak('rstudio/pagedown')
library(readr)
library(dplyr)
library(tidyverse)
library(ggplot2)
library(here)
here::i_am("poster-template.Rmd")
```

```{r, eval=F, include=FALSE}
pagedown::chrome_print("poster-template.Rmd")
```

# Abstract

We investigate racial disparities in U.S. incarceration rates and capital punishment to highlight systemic inequities within the criminal justice system. Our hypotheses align with research literature and historical data, indicating that Black Americans are incarcerated at disproportionately higher rates than other groups; we take a particular focus on southern states. We also examine racial bias in the administration of the death penalty, specifically analyzing data on Black defendants. By utilizing multiple sources of state-level data, we aim to uncover how race influences patterns of incarceration and sentencing, emphasizing the need for reforms to address persistent inequities and promote fairness in the justice system.

# Overview

This is some sample text.

# Literature Review

This is some sample text.

# Research Questions

1. This is research question 1.

2. This is research question 2.

# Methodology

This is some sample text.

## Data

This is some more sample text.

## Analytic framework

This is some more sample text.

# Findings

These are the findings.

Here is finding 1.

Here is finding 2.

```{r, include=F, warning=F, messages=F}
sentences <- read.csv("../data/sentences.csv")

yearly <- yearly_counts <- sentences %>%
  group_by(Year) %>%
  summarise(Count = n())
```

```{r, echo=F, warning=F, messages=F}
ggplot(yearly_counts, aes(x = Year, y = Count)) +
  geom_line(color = "blue") +
  geom_point(color = "red") +
  labs(title = "Trend of Sentences Over Time", x = "Year", y = "Count") +
  theme_minimal()
```

Here is finding 3.

Here is finding 4.

# Discussion

This is the discussion section [@alexander2021new].

This is the further discussion.

# Conclusion

This is some concluding text.

# Acknowledgements

These are the acknowledgements. This work was supporting by funding from the Alfred P. Sloan Foundation (Grant 2023-21062).

# References
